\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Gaurav}{Rawal}{ \urlstyle{same}\href{https://iamgrawal.netlify.app}{iamgrawal.netlify.app} |
\href{mailto:gaurav.rawal66@gmail.com}{gaurav.rawal66@gmail.com} | +918860832914
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\textbullet{} React.js \\
\textbullet{} Next.js \\
\textbullet{} Typescript \\
\textbullet{} Javascript \\
\textbullet{} Chakra UI\\
\textbullet{} Styled components \\
\textbullet{} GraphQL\\
\textbullet{} REST API\\
\textbullet{} Redux \\
\textbullet{} Node.js \\
\textbullet{} HTML/CSS \\
\textbullet{} Jest/Enzyme \\
\textbullet{} React Testing Library \\
\textbullet{} Git\\
\location{\custombold{Limited Experience:}}
\textbullet{} Python \\
\textbullet{} Django \\
\textbullet{} Vue.js \\
\textbullet{} Ruby on Rails \\
\textbullet{} Express \\
\textbullet{} Firebase
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Portfolio: \href{https://iamgrawal.netlify.app}{\custombold{iamgrawal.app}} \\
Github: \href{https://github.com/iamgrawal}{\custombold{iamgrawal}} \\
LinkedIn:  \href{https://www.linkedin.com/in/iamgrawal}{\custombold{iamgrawal}} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Guru Gobind Singh Inderprastha \linebreak University}
\descript{B.Tech in Computer Science}
\location{Aug 2015-19 | New Delhi, IN}
CGPA: 8.01/10.00
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.71\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-2mm}
\section{Experiences}

\runsubsection{Arcana Analytics}
\descript{| Founding Software Engineer | July 2022 – Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led development of a fintech platform for institutional investors, focusing on portfolio risk analysis, performance decomposition, and crowding analysis.
\item Established initial project architecture using \custombold{Next.js with TypeScript}, integrated \custombold{Chakra UI} for design systems, and implemented \custombold{Highcharts} for data visualization.
\item Developed key features including sector mapping component, real-time news aggregation, and customizable dashboards for user-specific widgets.
\item Spearheaded product pivot from crypto to Traditional Finance assets, implementing comprehensive portfolio management system with 13F filings and ETF data integration.
\item Enhanced charting capabilities with advanced financial metrics, diverse chart types, and data transformations.
\item Optimized performance by migrating from React Table to Glide apps, improving grid performance for large datasets.
\item Ensured accessibility compliance and implemented user-friendly features like auto-refreshing and pagination.
\end{tightemize}
\sectionsep

\runsubsection{Tesco}
\descript{| Software Engineer | Nov 2020 – June 2022}
\begin{tightemize}
\item Developed a \custombold{one-stop multi-regional help-desk platform} for all the daily work which allowed users to setup and manage their account, raise and manage requests, apply for software catalogues and search for guides and articles.
\item Moved the platform from multi-repo application to \custombold{mono-repo} application with common \custombold{UI libraries} for applications using \custombold{styled components and react}.
\item Created an \custombold{Admin portal} for the product managers, that reduced the dependency on engineering team by \custombold{60\%}.
\end{tightemize}
\sectionsep

\runsubsection{Unilodgers}
\descript{| Software Engineer | August 2019 - Nov 2020}
\begin{tightemize}
\item Created a \custombold{multi-user Whatsapp client} using \custombold{React and Phoenix} to manage the support platform.
\item Added \custombold{SSR} to complete \custombold{CSR} react code.
\item Performed \custombold{cross accounts - cross regions system migration} on AWS account with \custombold{zero downtime}.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERNSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-2mm}
\section{Internships}
\runsubsection{Auquan}
\descript{| Full Stack Developer Intern | Jan 2019 – May 2019}
\begin{tightemize}
\item Developed a data science competition platform using \custombold{react.js and node.js}.
\item Created a dashboard for business clients to onboard and manage quant analysis, also consisting of an inhouse \custombold{data visualiser} library built in \custombold{react}.
\end{tightemize}
\sectionsep

\runsubsection{Camp K12}
\descript{| Full Stack Developer Intern | May 2018 – Oct 2018}
\begin{tightemize}
\item Developed an online \custombold{browser based IDE} for beginners to learn AI using building blocks, with the ability to create models on the client side itself.
\item Created an \custombold{event dashboard platform} for a block chain event with features like public forum, user profile management, leader board.
\end{tightemize}
\sectionsep

\runsubsection{Brandlitic}
\descript{| Full Stack Developer Intern | Dec 2017 – May 2018}
\begin{tightemize}
\item Worked on Pixorr, a chrome extension search engine for design assets, and developed \custombold{web crawlers, chrome extension, and admin dashboard} using JavaScript libraries.
\end{tightemize}
\sectionsep
\end{minipage} 
\begin{minipage}[t]{0.25\textwidth}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
\textbullet{} \custombold{Speaker \& Judge} at various events\\
\textbullet{} \custombold{Event Host:} Devfest India 2021\\
\textbullet{} \custombold{Event Host:} Chrome Developer Summit Extended 2021\\
\textbullet{} \custombold{Community Organiser:} Google Developer Groups, New Delhi(2019-Present)\\
\textbullet{} \custombold{Chairperson:} at IIPC, The Entrepreneurship Cell, GTBIT (2018-2019)\\
\textbullet{} \custombold{Web Development Head:} at IEEE, GTBIT (2018-2019)\\
\textbullet{} \custombold{Hackathon Runner-up:} Cyber Security Hackathon By US Embassy 2017\\
\textbullet{} \custombold{Hackathon Runner-up:} Smart India Hackathon 2017\\
\textbullet{} \custombold{Hackathon Runner-up:} NPC India Hackathon 2016\\
\textbullet{} \custombold{Runner-up:} at Bug swat competition in Gates 2k16, cultural fest of GTBIT.\\
\sectionsep
\end{minipage}
\hfill
\begin{minipage}[t]{0.71\textwidth}   

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-2mm}
\section{Projects} 
\runsubsection{Devfest India 2021}
\descript{| \href{https://devfestindia.com}{\bf Link}}
\location{Tech Stack - Vue.js, Node.js, Firestore, GCP Compute Engine, Google Data Studio, Redis DB}
\vspace*{4mm}
\begin{tightemize}
\item Developed a conference application for Devfest India that is used to register users, create/edit user profile, create social badge and create/manage job listings, and has an admin dashboard to manage push notifications, send emails using Send Grid, and check analytics.
\end{tightemize}
\sectionsep

\runsubsection{WhatsApp Client}
\descript{| \href{https://github.com/iamgrawal/whatsapp-business-api}{\bf Link}}
\location{Tech Stack - Node.js, Gupshup whatsapp api}
\begin{tightemize}
\item Created a whatsapp node client script to send messages, add media(images, videos, documents) to single or multiple users at once using Gupshup api.
\end{tightemize}
\sectionsep

\runsubsection{Music Maker}
\descript{| \href{https://github.com/iamgrawal/react-masterclass}{\bf Link}}
\location{Tech Stack - React.js. Node.js, Socket.io}
\begin{tightemize}
\item Created a collaborative platform where users can generate various instrumental sounds along with multiple users simultaneously.
\end{tightemize}
\sectionsep

% \runsubsection{AI Playground}
% \descript{| \href{https://ai.campk12.com/}{\bf link}}
% \location{Tech Stack - React.js, Redux, Firebase cloud store}
% \begin{tightemize}
% \item Created an online web IDE for users to learn AI that supports building client side AI models, using pre-built models, cloud sync, and real-time compilation.
% \end{tightemize}
% \sectionsep

% \runsubsection{Multi user WhatsApp Client}
% \descript{}
% \location{Tech Stack - React.js, Twilio, Pheonix}
% \begin{tightemize}
% \item Created WhatsApp Client for multi-user chat, imitating the support system, using React Pheonix and Twilio WhatsApp APIs.
% \end{tightemize}
% \sectionsep
\end{minipage}
\end{document}
